Strings functions analysis

### 2022-08-28 article.tex
all ruby functions added

>>>>

    \textbf{Ruby}: new, try\_convert, \%, *, +, +@, -@, <<, <=>, ==, ===, =~, [], []=, ascii\_only\?, b, bytes, bytesize, byteslice, capitalize, capitalize!, casecmp, casecmp\?, center, chars, chomp, chomp!, chop, chop!, chr, clear, codepoints, concat, count, crypt, delete, delete!, delete\_prefix, delete\_prefix!, delete\_suffix, delete\_suffix!, downcase, downcase!, dump, each\_byte, each\_char, each\_codepoint, each\_grapheme\_cluster, each\_line, empty\?, encode, encode!, encoding, end\_with\?, eql\?, force\_encoding, freeze, getbyte, grapheme\_clusters, gsub, gsub!, hash, hex, include\?, index, initialize\_copy, insert, inspect, intern, length, lines, ljust, lstrip, lstrip!, match, match\?, next, next!, oct, ord, partition, prepend, replace, reverse, reverse!, rindex, rjust, rpartition, rstrip, rstrip!, scan, scrub, scrub!, setbyte, size, slice, slice!, split, squeeze, squeeze!, start\_with\?, strip, strip!, sub, sub!, succ, succ!, sum, swapcase, swapcase!, to\_c, to\_f, to\_i, to\_r, to\_s, to\_str, to\_sym, tr, tr!, tr\_s, tr\_s!, undump, unicode\_normalize, unicode\_normalize!, unicode\_normalized\?, unpack, unpack1, upcase, upcase!, upto, valid\_encoding\?.
